\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.5}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage[normalem]{ulem}
\usepackage{revnum}%ethertex-once: http://www.math.harvard.edu/graduate/vitae/revnum.sty
\usepackage{fancyhdr}
\usepackage{hyphenat}
\usepackage[T1]{fontenc}
\usepackage[oldstylenums,rmx,largesmallcaps]{kpfonts}
\usepackage[protrusion=true,expansion=auto]{microtype}
\definecolor{MyDarkBlue}{rgb}{0.033,0,0.33} 
\usepackage[
  letterpaper=true,breaklinks=true,colorlinks=true,linkcolor=black,%
citecolor=black,urlcolor=MyDarkBlue,bookmarks=false,bookmarksopen=false,%
  pdfauthor={},%
  pdftitle={CV - J. Alex Halderman},%
  pdftex]{hyperref}

\pdfglyphtounicode{zerooldstyle}{0030}
\pdfglyphtounicode{oneoldstyle}{0031}
\pdfglyphtounicode{twooldstyle}{0032}
\pdfglyphtounicode{threeoldstyle}{0033}
\pdfglyphtounicode{fouroldstyle}{0034}
\pdfglyphtounicode{fiveoldstyle}{0035}
\pdfglyphtounicode{sixoldstyle}{0036}
\pdfglyphtounicode{sevenoldstyle}{0037}
\pdfglyphtounicode{eightoldstyle}{0038}
\pdfglyphtounicode{nineoldstyle}{0039}
\pdfgentounicode=1

\begin{document}

\fancyhead{}
\fancyfoot[F]{\hfill\small\thepage}
\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancy}\thispagestyle{fancy}
\newcommand{\cvsection}[1]{%
  {\vspace{8pt}{\Large\bf #1}}}
\newdimen{\leftsize}
\newdimen{\rightsize}
\leftsize=0.5in
\rightsize=5.5in
\parindent=0pt
\setlength{\leftmargini}{\leftsize}
\addtolength{\leftmargini}{3pt}
\renewcommand{\labelenumi}{[\arabic{enumi}]}
\urlstyle{rm}
\def\textsb#1{{\fontseries{sb}\selectfont #1}}

\newif\ifsocial\socialfalse
{\parbox[b]{3.55in}{
\fontsize{18pt}{22pt}\selectfont
\textbf{\textls[15]{Matthew \kern2.5pt Bernhard}}\vspace{2pt}

\setlength\leftskip{0pt}\setlength\rightskip{-\leftskip}\setlength\parfillskip{\leftskip}
\raggedright

\fontsize{12pt}{16pt}\selectfont
Ph.D. Candidate, Computer Science and Engineering\\
{\textsl{University of Michigan}}
}}
\hfill
{\parbox[b]{2.0in}{\raggedleft\fontsize{10pt}{12pt}\selectfont
\textls[40]{2260 Hayward Street}\\
\textls[-30]{Ann Arbor, \textsc{mi} 48109 \textsc{usa}}\vspace{1pt}
\textls[10]{matber@umich.edu}}
\vspace{8pt}

{\fontsize{12pt}{16pt}\selectfont
    \textls[20]{{\today}}\hfill
\textls[20]{%
        \href{http://mbernhard.com}{mbernhard.com}%
    }%
}
}

\normalsize\selectfont
\smallskip

\setstretch{1.1}

\vspace*{8pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Research Overview}
\vspace{-2pt}

\begin{itemize}[label={},leftmargin=0.25in,labelsep=0pt]\addtolength{\itemsep}{-0.25\baselineskip}

\item My research focuses on areas where the security and privacy implications of sophisticated systems impacts users in the real world. My interests include election security, usability, human-computer interaction, censorship measurement and resistance, Internet measurement, cryptography, statistics, and systems security. I'm also interested in the intersection of computer science, psychology, politics, and policy.

\end{itemize}

\cvsection{Education}
\begin{itemize}[label={--\ },leftmargin=0.25in,labelsep=0.1625em]\addtolength{\itemsep}{-0.25\baselineskip}

        \item Ph.D in Computer Science, University of Michigan, Expected Spring 2021\\
        Advisor: J. Alex Halderman
		
        \item M.S. in Computer Science, University of Michigan, Summer 2018

        \item B.A. in Computer Science, Rice University, Spring 2015\\
        Advisor: Dan S. Wallach
        
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Refereed Conference Publications}
\begin{enumerate}[leftmargin=0.25in,labelsep=0.25em,resume]
\addtolength{\itemsep}{-0.25\baselineskip}

\item
\textsb{\href{https://mbernhard.com/papers/https-chi19.pdf}{On the Usability of HTTPS Deployment}}\\
\uline{Matthew Bernhard}, Jonathan Sharman, Claudia Ziegler Acemyan, Philip Kortum, Dan S. Wallach, and J.~A.~Halderman\\
To appear in {\em Proc.\ ACM Conference on Human Factors in Computing Systems} (CHI), May 2019.\\
Acceptance rate: 24\%, 705/2958.

\item
\textsb{\href{https://ensa.fi/papers/403forbidden_imc18.pdf}{403 Forbidden: A Global View of Geoblocking}}\\
Allison McDonald, \uline{Matthew Bernhard}, Luke Valenat, Benjamin VanderSloot, Will Scott, Nick Sullivan, J.~A.~Halderman, and Roya Ensafi\\
{\em Proc.\ 18th ACM Internet Measurement Conference} (IMC), October 2018.\\
Acceptance rate: 24\%, 43/174.

\item
\textsb{\href{https://arxiv.org/abs/1707.08619}{Public Evidence from Secret Ballots}}\\
\uline{Matthew Bernhard}, Josh Benaloh, J.~A. Halderman,  Ronald L. Rivest, Peter Y. A. Ryan, Philip B. Stark, Vanessa Teague, Poorvi L. Vora, and Dan S. Wallach\\
{\em Proc. 2nd International Joint Conference on Electronic Voting} (E-Vote-ID), Bregenz, Austria, October 2017.

\item
\textsb{\href{https://mbernhard.com/papers/mirai-sec17.pdf}{Understanding the Mirai Botnet}}\\
Manos Antonakakis, Tim April, Michael Bailey, \uline{Matthew Bernhard}, Elie Bursztein, Jaime Cochran, Zakir Durumeric, J.~A. Halderman, Luca Invernizzi, Michalis Kallitsis, Deepak Kumar, Chaz Lever, Zane Ma, Joshua Mason, Damian Menscher, Chad Seaman, Nick Sullivan, Kurt Thomas, and Yi Zhou\\
{\em Proc.\@ 26th USENIX Security Symposium}, Vancouver, BC, August 2017.\\
Acceptance rate: 16\%, 85/522.

\item
\textsb{\href{https://mbernhard.com/papers/kiosk-pst16.pdf}{Implementing Attestable Kiosks}}\\
\uline{Matthew Bernhard}, J.~A. Halderman, and Gabe Stocco\\
{\em Proc.\ 14th IEEE Conference on Privacy, Security, and Trust} (PST), Auckland, NZ, December 2016.

\item
\textsb{\href{https://mbernhard.com/papers/https-perspectives-imc16.pdf}{Towards a Complete View of the Certificate Ecosystem}}\\
Benjamin VanderSloot, Johanna Amann, \uline{Matthew Bernhard}, Zakir Durumeric, Michael Bailey, and J.~A. Halderman\\
{\em Proc.\ 16th ACM Internet Measurement Conference} (IMC), Santa Monica, November 2016.\\
Acceptance rate: 25\%, 46/184.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Refereed Workshop Publications}
\begin{enumerate}[leftmargin=0.25in,labelsep=0.25em,resume]
\addtolength{\itemsep}{-0.25\baselineskip}

\item
\textsb{\href{https://fc19.ifca.ai/voting/papers/OBHRS19.pdf}{Bernoulli Ballot-Polling: A Manifest Improvement for Risk-Limiting Audits}}\\
Kellie Ottoboni, \uline{Matthew Bernhard}, J.~A.  Halderman, Ronald L. Rivest, and Philip B. Stark\\
{\em Proc.\@ 4th Workshop on Advances in Secure Electronic Voting}, Feb.\ 2019.

\item
\textsb{\href{https://mbernhard.com/papers/recount2016.pdf}{Voting Technologies, Recount Methods and Votes in Wisconsin and Michigan in 2016}}\\
Walter Mebane and \uline{Matthew Bernhard}\\
{\em Proc.\@ 3th Workshop on Advances in Secure Electronic Voting}, Feb.\ 2018.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\cvsection{Selected Other Publications}
\begin{enumerate}[leftmargin=0.25in,labelsep=0.25em,resume]
\addtolength{\itemsep}{-0.25\baselineskip}


\item
\textsb{\href{http://spectrum.ieee.org/tech-talk/telecom/security/the-security-challenges-of-online-voting-have-not-gone-away}{The Security Challenges of Online Voting Have Not Gone Away}}\\
Robert Cunningham, \uline{Matthew Bernhard}, and J.~A. Halderman\\
\emph{IEEE Spectrum}, November 3, 2016.

\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Speaking}
\vspace{8pt}

\textsb{\large Major Invited Talks and Keynotes}
\vspace{-6pt}
\begin{itemize}[label={--\ },leftmargin=0.25in,labelsep=0.1625em]
\addtolength{\itemsep}{-0.25\baselineskip}

\item
\textsb{\href{}{Michigan Advisory Committee to the U.S. Commission on Civil Rights}}\\
Testimony before the Michigan Advisory Committee to the U.S. Commission on Civil Rights regarding the security of voter registration systems in Michigan, April 30, 2019.

\item
\textsb{\href{}{A Crash Course in Election Security}}\\
DEF CON Voting Village, August 10, 2018.

\item\textsb{\href{}{Recount 2016: An Uninvited Security Audit of the U.S. Presidential Election}}\\
RoadSec, S\~ao Paulo, November 11, 2017.

\item\textsb{\href{https://media.ccc.de/v/33c3-8074-recount_2016_an_uninvited_security_audit_of_the_u_s_presidential_election}{Recount 2016: An Uninvited Security Audit of the U.S. Presidential Election}}\\
33c3, Hamburg, December 28, 2016.
\end{itemize}

\textsb{\large Selected Talks}\:
\vspace{-6pt}
\begin{itemize}[label={--\ },leftmargin=0.25in,labelsep=0.1625em]
\addtolength{\itemsep}{-0.4\baselineskip}

\item\textsb{Cybersecurity and U.S. Elections}\\
Invited speaker, RoadSec Pro, S\~ao Paulo, November 10, 2017;
Invited speaker, Workshop on Electoral Technologies, Brasilia, November 6, 2017;

\item\textsb{Internet Pinball: The Security and Privacy Impact of Redirects}\\
Mozilla Security Research Summit, San Francisco, May 24th 2019.

\item\textsb{Election Security and You}\\
Midwest Security Workshop, Chicago, April 13, 2019.

\item\textsb{Coercion-resistant, Receipt-free, and Paperless Voting}\\
Rump session talk at Financial Cryptography, St. Kitts, 2019.

\item\textsb{403 Forbidden: A Global View of Geoblocking}\\
Rump session at the 9th USENIX Workshop on Free and Open Communications on the Internet (FOCI '18), Baltimore, 2018.

\item\textsb{A Constitutional Argument Against Burr-Feinstein}\\
Rump session at the 25th USENIX Security Symposium (USENIX '16), Austin, 2016.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\vspace{-6pt}
\cvsection{Advising and Mentoring}
\vspace{8pt}
%\vspace{-3pt}

\textsb{\large Undergraduate Independent Work}
\vspace{-5pt}
\begin{itemize}[label={--\ },leftmargin=0.65in,labelsep=0.325em]
\addtolength{\itemsep}{-0.525\baselineskip}

\item[--\ 2019:] Henry Meng, Jensen Hwa, Thea Lau, Chand Rajendra-Nicolucci, Antonio Atkinson, Jeremy Wink, Kartikey Kandula
\item[--\ 2018:] Henry Meng, Jensen Hwa



\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Teaching}
\vspace{-6pt}

\begin{itemize}[label={--\ },leftmargin=0.25in,labelsep=0.1625em]
\addtolength{\itemsep}{-0.4\baselineskip}


\item\textsb{Graduate Student Instructor \href{https://www.eecs.umich.edu/courses/eecs498.009/}{Election Cybersecurity}}, EECS 498, University of Michigan, Fall~2018.\\
   {\small Assisted with design and teaching of an undergraduate research course into election security. Lectured, wrote homework assignments, and oversaw ten undergraduate independent research projects.}

\item\textsb{Graduate Student Instructor, \href{https://www.eecs.umich.edu/courses/eecs388/}{Introduction to Computer Security}}, EECS 388, University of Michigan, Winter 2018. 

\item
\textsb{Course Operations Liaison \href{https://www.coursera.org/learn/digital-democracy}{Securing Digital Democracy}}, Coursera (MOOC)\\
    {\small Assisted with content maintenance and day-to-day course operations for a massive, open online course about electronic voting and Internet voting technologies.}
    
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage

\cvsection{Professional Service}
\vspace{8pt}

\textsb{\large Program Committee}
\vspace{-6pt}

\begin{itemize}[label={--\ },leftmargin=0.25in,labelsep=0.1625em]
\addtolength{\itemsep}{-0.5\baselineskip}
\item \textbf{Program co-chair}, 
6th Workshop on Advances in Secure Electronic Voting, 2020.
\item \textbf{Program co-chair}, 
5th Workshop on Advances in Secure Electronic Voting, 2019.
\end{itemize}

\textsb{\large External Reviewer}
\vspace{-6pt}
\begin{itemize}[label={--\ },leftmargin=0.25in,labelsep=0.1625em]
\addtolength{\itemsep}{-0.5\baselineskip}

\item 2019 USENIX Security Symposium (USENIX '19)
\item 2018 ACM Internet Measurement Conference (IMC '18)
\item 2018 ACM Conference on Computer and Communications Security (CCS '18)
\item 2018 International Symposium on Research in Attacks, Intrusions, and Defenses (RAID '18)
\item 2017 ACM Conference on Computer and Communications Security (CCS '17)
\item 2017 Network and Distributed System Security Symposium (NDSS '17)
\item 2016 IEEE Conference on Privacy, Security, and Trust (PST '16)
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Broader Impact of Selected Projects}
\begin{itemize}[label={--\ },leftmargin=0.25in,labelsep=0.1625em]
\addtolength{\itemsep}{-0.25\baselineskip}
\setstretch{0.975}

\item\textsb{\href{https://www.theoaklandpress.com/news/local/rochester-hills-to-conduct-post-election-audit/article_593f0ba0-f324-11e8-9b5f-2f927d645982.html}{Implementing Better Election Security}} (2018--2019)\\
{\small Currently working with the State of Michigan and municipalities across the state to pilot risk-limiting audits to help secure Michigan's elections. Developed software that interfaces with voting technology to enable ballot comparison audits.}

\item\textsb{\href{https://www.ftc.gov/news-events/press-releases/2017/01/ftc-charges-d-link-put-consumers-privacy-risk-due-inadequate}{Fighting Weak IoT Security}} (2017)\\
{\small Applied machine learning techniques to Internet measurement data to identify make and model of consumer devices that were infected by the Mirai botnet. Data has been used in ongoing legal proceedings by the Federal Trade Commission to encourage U.S. manufacturers to improve the default security of their devices.}
\item\textsb{\href{https://newrepublic.com/article/140254/inside-story-trump-clinton-stein-presidential-election-recount}{2016 U.S. Presidential Election Recounts}} (2016)\\
{\small Supported efforts to detect vote manipulation in the 2016 election in Michigan, Wisconsin, and Pennsylvania. While progress was hindered and in places entirely halted due to political and legal reasons, what little evidence htat was generated did not show that the 2016 Presidential election was fraudulent.}
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Professional Experience}
\begin{itemize}[label={--\ },leftmargin=0.25in,labelsep=0.1625em]
\addtolength{\itemsep}{-0.25\baselineskip}
\setstretch{0.975}

\item\textsb{\href{https://verifiedvoting.org}{Data Science Consultant for Verified Voting}} (2018--present)\\
{\small Collecting and interpreting data on currently certified voting equipment in the United States to empower municipalities to make intelligent purchasing decisions. Focus on the cyber security impacts of voting technology.}

\item\textsb{Expert Witness} (2018--present)\\
{\small Served as an expert witness in several lawsuits opposing the use of direct-recording electronic voting machines. {\it \href{https://www.theroot.com/brian-kemp-doesnt-need-to-rig-georgias-election-beca-1830233656}{Curling v. Kemp}}, {\it \href{https://www.apnews.com/b3e8f250f50244478ae3bbf19399f6ff}{CGG v. Crittenden}}, {\it {\href{https://www.pacermonitor.com/public/case/25902838/Shelby_Advocates_for_Valid_Elections_et_al_v_Hargett_et_al}{Shelby Advocates for Valid Elections et al. v. Hargett et al.}}}}

\item\textsb{\href{https://cloudflare.com}{Cryptography Intern, Cloudflare}} (2017)\\
{\small Developed Certificate Transparency monitoring features. Also built an SSL detector to determine what SSL settings customer sites can support, under the advising of Nick Sullivan.}

\item\textsb{\href{https://www.microsoft.com/en-us/research/}{Microsoft Research Intern}} (2015)\\
{\small Explored applications of trusted platform modules (TPMs) in voting through interfaces provided by Windows 10 under the advising of Josh Benaloh.}

\end{itemize}

\end{document}
